### 2014-04-23 Response_to_R0_Reviews.tex

    \textbf{\input{mr_dwi_dce_methods}}

    The contrast agent that was used has also been added to the manuscript.

    \item \textit{Please describe what is meant by the "longitudinal array" (pg
            6 line 151) and specify that the ER7B is an endorectal transducer.
            This was stated in the associated figure caption but not in the
            text.  Also, please state more clearly in the text that ARFI
            imaging was performed endorectally.}

    We have modified the text describing the ER7B array as follows:

    \textbf{\ldots side-fire array of an Acuson ER7B endorectal transducer.}

    We have also emphasized that the imaging was performed endorectally by
    modifying the following statement in the same section:

    \textbf{3D volumetric imaging data was acquired endorectally\ldots}

### 2014-04-23 arfi_methods.tex
emphasized that the ER7B uses a side-fire array and is used endorectally

\subsection{ARFI Imaging}
Experimental ARFI imaging data were acquired using a modified Siemens Acuson
SC2000\texttrademark~ultrasound scanner (Siemens Healthcare, Ultrasound Business Unit,
Mountain View, CA, USA) and the longitudinal array of an Acuson ER7B
transducer.  The ARFI imaging sequence was comprised of
standard B-mode ultrasonic imaging, or tracking beams, and pushing beams. For
each lateral location, two pre-push reference images were acquired, then three
300 cycle pushing pulses were transmitted in rapid succession, focused at 30
mm, 22.5 mm, and 15 mm, respectively, and finally the response of the tissue
was tracked for up to 6 ms at a PRF of 8kHz. This pushing strategy is similar to
what has been published by Bercoff \etal~\cite{Bercoff2004}. The 30 mm and 22.5
mm foci pushing pulses were transmitted at 4.6 MHz with a F/2 geometry and the
15 mm focus pushing pulse was transmitted at 5.4 MHz with a F/2.35 geometry to
maintain the same beamwidth (0.67 mm) throughout the region of excitation. A
total of 82 lateral locations were interrogated to cover the 55 mm field of
view, translating 0.67 mm laterally per location.

@@

3D volumetric imaging data was acquired using mechanical rotation of the ER7B
transducer between sequential imaging frames, sweeping across the lateral
extent of the prostate.  This rotation setup utilized a CIVCO
Micro-Touch\texttrademark stabilizer (CIVCO Medical Solutions, Kalona, IA USA)
that allows for complete 6-axis degrees of freedom for manual positioning of
the transducer to sweep through the entire prostate during imaging.  Sequential
imaging frames were $\sim$1\degree apart, depending on the absolute size of the
prostate.  A custom optical angular feedback transduction circuit utilizing a
reflective linear strip with 212 lines-per-inch (LPI) resolution (US Digital,
Vancouver, WA, USA) with a QSB-S Quadrature-to-USB adapter to achieve 9 line /
degree resolution.  Rotation was performed with a 141 oz-in torque stepper
motor with planetary gearbox (Model \#11YPG202S-LW4-R27, Anaheim Automation,
Anaheim, CA, USA) (Figure~\ref{fig:setup_annotated}) to achieve accurate
spatial localization of the imaging frames in the 3D dataset.

>>>>

\subsection{ARFI Imaging}
Experimental ARFI imaging data were acquired using a modified Siemens Acuson
SC2000\texttrademark~ultrasound scanner (Siemens Healthcare, Ultrasound Business Unit,
Mountain View, CA, USA) and the \textbf{side-fire array of an Acuson ER7B
endorectal transducer}.  The ARFI imaging sequence was comprised of
standard B-mode ultrasonic imaging, or tracking beams, and pushing beams. For
each lateral location, two pre-push reference images were acquired, then three
300 cycle pushing pulses were transmitted in rapid succession, focused at 30
mm, 22.5 mm, and 15 mm, respectively, and finally the response of the tissue
was tracked for up to 6 ms at a PRF of 8kHz. This pushing strategy is similar to
what has been published by Bercoff \etal~\cite{Bercoff2004}. The 30 mm and 22.5
mm foci pushing pulses were transmitted at 4.6 MHz with a F/2 geometry and the
15 mm focus pushing pulse was transmitted at 5.4 MHz with a F/2.35 geometry to
maintain the same beamwidth (0.67 mm) throughout the region of excitation. A
total of 82 lateral locations were interrogated to cover the 55 mm field of
view, translating 0.67 mm laterally per location.

@@

\textbf{3D volumetric imaging data was acquired endorectally} using mechanical
rotation of the ER7B transducer between sequential imaging frames, sweeping
across the lateral extent of the prostate.  This rotation setup utilized a
CIVCO Micro-Touch\texttrademark stabilizer (CIVCO Medical Solutions, Kalona, IA
USA) that allows for complete 6-axis degrees of freedom for manual positioning
of the transducer to sweep through the entire prostate during imaging.
Sequential imaging frames were $\sim$1\degree apart, depending on the absolute
size of the prostate.  A custom optical angular feedback transduction circuit
utilizing a reflective linear strip with 212 lines-per-inch (LPI) resolution
(US Digital, Vancouver, WA, USA) with a QSB-S Quadrature-to-USB adapter to
achieve 9 line / degree resolution.  Rotation was performed with a 141 oz-in
torque stepper motor with planetary gearbox (Model \#11YPG202S-LW4-R27, Anaheim
Automation, Anaheim, CA, USA) (Figure~\ref{fig:setup_annotated}) to achieve
accurate spatial localization of the imaging frames in the 3D dataset.
